---
title: '"Homework # 12 ggplot"'
author: "H24061260"
output: html_document
---
---

title: "Homework # 12 ggplot"

author: yourID

output: html_document

---



```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = F, fig.align='center')

library(ggplot2)

```



`mpg` is the dataset that comes with ggplot.  You can use `View(mpg)` to get an overview of the dataset. 



1. Using the `mpg` dataset generate a scatter plot of `cty` (city mileage) and `hwy` (highway mileage).

```{r}
qplot(cty,hwy,data=mpg,xlab="City mileage", ylab="Highway mileage")
```


2. Add a colour scale to the scatterplot based on the `displ` variable (engine displacement in liters).

```{r}
qplot(cty,hwy,data=mpg,xlab="The average city mileage", ylab="The average highway mileage",colour = displ)
```


3. Using the `mpg` dataset recreate the plot as shown below.

```{r}
#qplot(cty,hwy,data=mpg,xlab="The average city mileage", ylab="The average highway mileage",colour = drv)
```

```{r}
(ggplot(mpg, 

        aes(x=cty, y=hwy, 

            color=drv))

        + geom_point() 

        + stat_smooth(method='lm') 

        + theme_bw())
```

4. Split the `cty` vs hwy plot into a grid of plots separated by `drv`. 

```{r}
qplot(x=cty, y=hwy, data = mpg, facets =  .~ factor(drv) ,xlab="City mileage",ylab="Highway mileage")
```


5. Generate a boxplot of `cty` comparing `drv` (f=front wheel, r=rear wheel, 4=4 wheel).

```{r}
qplot(x=drv,y=cty, data=mpg, geom =c("boxplot"))
```


6. Generate density plots of `hwy` coloured by `drv`.  

```{r}
qplot(hwy, data=mpg, geom ="density", fill=drv, alpha=I(1/3))
```


7. Generate a boxplot of `cty` comparing type of transmission (automatic v.s. manual)

```{r}
qplot(x=trans,y=cty, data=mpg, geom =c("boxplot","point","jitter"),xlab="Transmission",ylab="City mileages")
```